True versus apparent shapes of astrophysical bow shocks

### 2016-06-10 papers/Paper1/proplyd-bowshocks.tex
New start on Jorge's paper
Paper1 - fix {array} envs and untrack .log, .pdf
Paper1: Add bibliography and make start on intro
All references should go in bowshocks-biblio.bib
Add short title and author list
Also, define commands for the cos/cosh terms in the conic section
equations.  Try out using cursive upper case letters, but we may change
those later
More on bow shocks for intro
Mention jet-driven bow shocks.  Add a lot of references. Also first para
of abstract
Add table to paper of arc parameters from fits
Change CRyA to IRya

\documentclass[useAMS,usenatbib]{mn2e}

@@

% Standard LaTeX packages
\usepackage[varg]{txfonts}
% \usepackage[varg]{newtxmath}
% \usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{color}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

@@

\title{Photoionized bow shock shells.  I. Wind-wind interactions in the Orion proplyds}

\newcommand\AddressCRyA{Centro de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}

\section{Conclusions}
\label{sec:conc}

@@

>>>>

\RequirePackage{amsmath}
\documentclass[useAMS,usenatbib]{mn2e}

@@

% Standard LaTeX packages
\usepackage[varg]{txfonts}
% \usepackage[varg]{newtxmath}
% \usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{color}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

@@

\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  We develop a general framework for the effects of viewing angle on
  the apparent shape of a limb-brightened, cylindrically symmetric
  curved shock (bow shock).  
\end{abstract}

\input{sec-intro}
\input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-application}
\input{sec-conclusions}

%% TODO Investigate newer versions of BST file from
%% https://github.com/timj/mn2e-bst
\bibliographystyle{mn2e}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
